OSF management

### 2022-04-19 osf/manage-osf.Rmd
✨ - add code to upload analytic responses to osf

>>>>

# Upload analytic questionnaire answers.

Ugly code to do the job quickly. Need a-fixing.

```{r upload-analytic-responses}
teams_analyses <- read_csv("data/questionnaires/msa_data_analysis_questionnaire_cleaned.csv")

teams <- teams_analyses$Q17
teams_files <- paste0(teams, ".txt")

for (team in 1:length(teams)) {
  file_path <- glue("data/questionnaires/msa_data_analysis_files/{teams[team]}.txt")
  osf_upload(teams_comps[which(teams_comps$name == teams[team]),], path = file_path, verbose = T, conflicts = "overwrite")
}
```

```{r delete-analytic-responses}
for (team in teams) {
  file_name <- glue("{team}.txt")
  file_id <- osf_ls_files(teams_comps[which(teams_comps$name == team),], pattern = ".txt")
  if (nrow(file_id) > 0) {
    for (file in 1:nrow(file_id)) {
      if (file_id$name[file] %in% teams_files) {
        osf_rm(file_id[file,], check = FALSE)
      }
    }
  }
}
```
